%-------------------------
% Resume in Latex
% Author : Andrew Ho
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
\usepackage{charter}
% \usepackage{helvet}
% \renewcommand{\familydefault}{\sfdefault}




\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \titlerule\vspace{-5pt}\scshape\center\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Andrew Ho} \\ \vspace{1pt}
    Irvine, CA 92620 \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 949-245-4519 ~ \href{mailto:x@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{andyminhtuanho@gmail.com}} ~
    \href{https://linkedin.com/in/andrewmnho/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/andrewmnho}}  ~
    \href{https://github.com/}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/anmho}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Irvine Valley College \normalfont{\small{-- Irvine, CA}}}{\normalfont{Computer Science}}
{B.S. June 2024}{\textbf{GPA 4.0/4.0}}
\resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
%\resumeSubHeadingListStart
\begin{multicols}{4}
    \begin{itemize}[itemsep=-5pt, parsep=3pt]
        \item\small Data Structures
        \item Software Engineering
        \item Algorithms
        \item Intro to A.I.
        \item Systems Programming
        \item Computer Architecture
    \end{itemize}
\end{multicols}
\vspace*{2.0\multicolsep}
%\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\vspace{-5pt}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{unicart - Shopping List Web App} $|$ \emph{Flask, Python, JS, PostgreSQL, Bootstrap, Ubuntu }}{September 2021}
\resumeItemListStart
\resumeItem{ a web app where users can create, update, delete, and share product wishlists of products across all websites. }
\resumeItem{Utilizes web scraping to retrieve image metadata and for client rendering }
\resumeItem{Hosted on remote Ubuntu Linux Server using Linode.}
\resumeItemListEnd
\vspace{-13pt}

\resumeProjectHeading
{\textbf{Spicetracker - Recipe Sharing App} $|$ \emph{Java, Python, Parse, Heroku, Android Studio}}{Sept. 2021}
\resumeItemListStart
\resumeItem{Built an Android app that where users can post, share, and view other users recipes.}
\resumeItem{Worked with a team of four on a GitHub repository where I developed the logic of the Android App and machine learning recipe recommendation REST API hosted on Heroku.}
\resumeItem{Users can like, follow, and comment on other users posts.}
\resumeItemListEnd
\vspace{-13pt}

\resumeProjectHeading
{\textbf{Flixster - Movie Browsing App} $|$ \emph{Java, YouTube API, Android Studio}}{Sept. 2021}
\resumeItemListStart
\resumeItem{Developed an Android app that retrieves currently playing films and fetches movie data using TheMovieDB API.}
\resumeItem{Users can tap on a movie and retreive a description and view the trailer using YouTube API.}
\resumeItemListEnd

\vspace{-13pt}
\resumeProjectHeading
{\textbf{Simdemic - Pandemic Simulator} $|$ \emph{JavaScript, HTML, CSS}}{June 2021}
\resumeItemListStart
\resumeItem{Developed hackathon prototype pandemic simulation service web application.}
\resumeItem{Designed mathematical model to replicate virus spreading.}
\resumeItem{Created ability to adjust variables and factors to change simulation.}
\resumeItem{Pitched to hackathon judges as SaaS for governments agencies and businesses.}
\resumeItemListEnd
\vspace{-13pt}

\resumeProjectHeading
{\textbf{Instagram Clone} $|$ \emph{Java, Parse, Android Studio}}{Oct. 2021}
\resumeItemListStart
\resumeItem{Instagram Clone Android app using Java and Parse backend.}
\resumeItem{Users can post, sign up, sign in, and view their profile}
\resumeItemListEnd
\vspace{-13pt}

\resumeProjectHeading
{\textbf{MyDJ - Music Recommender} $|$ \emph{Python, matplotlib, NumPy, sci-kit-learn, pandas}}{July 2021}
\resumeItemListStart
\resumeItem{Designed and released a music genre prediction app based on user demographic and preferences using Python, matplotlib, NumPy, sci-kit-learn, and pandas.}
\resumeItemListEnd
\vspace{-13pt}

\resumeProjectHeading
{\textbf{AutoGH - GitHub Automatic Verifier} $|$ \emph{Python, Selenium}}{Aug. 2021}
\resumeItemListStart
\resumeItem{Built an automatic login and username verifier using Selenium and Python}
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-15pt}


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Love Yourself Clothing Startup}{Aug. 2018 -- Sept. 2019}
{Front End Web Developer}{Irvine, CA}
\resumeItemListStart
\resumeItem{Developed web store for local clothing startup brand using HTML CSS, and created a custom navigation bar}
\resumeItemListEnd

\resumeSubheading
{Phi Theta Kappa Honors Society}{Aug. 2021 -- Present}
{College Project}{Irvine, CA}
\resumeItemListStart
\resumeItem{Worked with school administration to bring a new leadership skills course to Irvine Valley College students.}
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-16pt}



%-----------PROGRAMMING SKILLS-----------
\section{Awards/Achievements}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
                    \textbf{Competitions }{\textbf{--} Winner of health\{hacks\} 2021 hackathon out of \textbf{178} participants. Designed a machine-learning pandemic simulation tool over 24 hours with JavaScript, HTML, CSS, MySQL. Presented to a panel of \textbf{9} Ivy League judges}} \\
        \textbf{Awards }{\textbf{--} AP Scholar w/ Distinction. Granted to students who receive an average score of at least 3.5 on all
            AP Exams taken, and scores of 3 or higher on five or more of these exams, IVC Dean's List} \\
    }
\end{itemize}
\vspace{-16pt}


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
                    \textbf{Languages}{: Python, JavaScript, Java, C, C\#, C++, HTML/CSS, PostgreSQL} \\
                    \textbf{Tools/Frameworks}{: Flask, React.js, Selenium, Ubuntu, sklearn, pandas, Visual Studio Code, Android Studio, Git, GitHub} \\
              }}
\end{itemize}
\vspace{-16pt}


\end{document}
